\documentclass[11pt,a4paper]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage[left=0.8in,top=0.8in,right=0.8in,bottom=0.8in]{geometry} 
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro} 
\usepackage{xcolor}      
\usepackage{titlesec}    
\usepackage{enumitem}    
\usepackage{parskip}     

%----------------------------------------------------------------------------------------
%	COLORS & STYLES
%----------------------------------------------------------------------------------------
\definecolor{titleblue}{HTML}{00199e} 
\definecolor{subtitleblue}{HTML}{2ec1e0} 
\definecolor{darktext}{HTML}{222222} 

\color{darktext}
\linespread{0.9} 
\setlength{\parskip}{0.1em} 

\titleformat{\section}{\Large\bfseries\color{titleblue}}{}{0em}{} 
\titlespacing*{\section}{0pt}{0.7em}{0.15em}

\newcommand{\blueitem}[1]{\textcolor{subtitleblue}{\textbf{#1}}}

\setlist[itemize]{label=\textbullet, leftmargin=*, noitemsep, topsep=0pt, parsep=0pt}

%----------------------------------------------------------------------------------------
%	DOCUMENT CONTENT
%----------------------------------------------------------------------------------------
\begin{document}

%--- HEADER ---
{\Huge \textbf{\textcolor{titleblue}{Vivek Joshi}}} \vspace{0.2em}

Pune, India \\
Mobile: +91 7798210595 \\
Email: vivekjoshi7798@gmail.com \\
LinkedIn: https://www.linkedin.com/in/vivek-joshi-77186a105/ \\
Nationality: India

\vspace{0.4em}

%--- PERSONAL PROFILE ---
\vspace{0.3cm}
\section*{Personal Profile}
\hrule
\vspace{0.2cm}
\quad Senior Backend Engineer with 6+ years of experience designing scalable, event-driven microservices using Java, Spring Boot, and Apache Kafka. Specialized in batch and real-time data ingestion pipelines, distributed systems, and financial derivative processing. Experienced in building production-grade systems deployed on Kubernetes with strong focus on observability, reliability, and performance.

%--- EDUCATION ---

\vspace{0.3cm}
\section*{Education}
\hrule
\vspace{0.2cm}
\blueitem{May, 2013 -- Jun, 2016: Diploma in Computer Technology} \\
\textit{P. R. E. C. Loni} \\
\textbf{Percentage:} 83.35% \\

\vspace{0.3em}

\blueitem{Jun 2016 -- Jun 2019: Bachelor of Engineering (B.E.) in Computer Technology } \\
\textit{Smt. Kashibai Navale College of Engineering (SKNCOE), Pune} \\
\textbf{CGPA:} 8.06 \\

%--- EXPERIENCE ---

\vspace{0.3cm}
\section*{Professional Experience}
\hrule
\vspace{0.2cm}
\blueitem{Aug 2019 -- Dec 2021: Software Developer} \\
\textit{Amdocs, Pune}
\begin{itemize}
\item Contributed to the development of a mission-critical Order Management System (OMS) used by global telecom service providers.
\item Developed backend services supporting customer onboarding, order lifecycle management, billing history tracking, and service status management.
\item Integrated OMS with CRM and retail front-end systems to enable seamless customer operations.
\item Implemented features for device provisioning and delivery, including broadband devices and TV set-top boxes.
\item Worked closely with QA and business teams to deliver stable releases in an Agile Scrum environment.
\item \textbf{Tech Stack :} Java 8, Spring Boot, Microservices, SQL, JPA, REST APIs
\end{itemize}

\vspace{0.3em}

\blueitem{Dec 2021 -- Jan 2024: Software Developer} \\
\textit{EPAM Systems, Pune}
\begin{itemize}
\item Designed and developed Spring Boot microservices platform for listed-derivatives data processing, distribution, and reconciliation using an event-driven architecture.
\item Implemented Apache Kafka-based streaming solutions, defining topic structure, partitioning, and retention strategies to enable reliable, and multi-consumer event processing.
\item Built domain services for data validation, enrichment, and reconciliation, ensuring end-to-end data integrity across distributed systems.
\item Exposed RESTful APIs for UI and external systems to access processed and aggregated derivatives data; implemented inter-service communication using REST.
\item Implemented Spring Cloud components (Eureka, API Gateway) and Resilience4j to enable centralized configuration, service discovery, and fault tolerance.
\item Containerized services with Docker and deployed on Kubernetes, leveraging ConfigMaps and Secrets for environment-specific configuration.
\item Enabled production observability through centralized logging and monitoring (Splunk) and used Kafka Streams for lightweight real-time transformations.
\item \textbf{Tech Stack :} Java, Spring Boot, Spring Cloud (Config Server, Eureka, API Gateway), Resilience4j, Apache Kafka, SQL, JPA, Docker, Kubernetes, REST APIs
\end{itemize}

\vspace{0.6em}

\blueitem{Jan 2024 -- Present: Senior Software Developer} \\
\textit{EPAM Systems, Pune}
\begin{itemize}
\item Designed and developed Kafka-based microservices ingesting listed-derivative product data from multiple external providers and publishing structured events for downstream systems.
\item Built real-time ingestion pipelines using IBM MQ and Apache Kafka, enabling low-latency event processing.
\item Implemented batch ingestion jobs to process daily OCC FIX-XML files, transforming them into domain-specific events.
\item Deployed and managed containerized services using Docker and Kubernetes.
\item Integrated centralized logging and monitoring using Splunk to improve observability and production support.
\item Collaborated with cross-functional teams in an Agile environment, ensuring timely and high-quality deliveries.
\item \textbf{Tech Stack :} Java, Spring Boot, Microservices, Apache Kafka, IBM MQ, Docker, Kubernetes, Splunk, REST APIs
\end{itemize}

%--- SKILLS ---

\vspace{0.3cm}
\section*{Skills}
\hrule
\vspace{0.2cm}

\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Languages:} Java 8/11/17
    \item \textbf{Frameworks:} Spring Boot, JPA, Hibernate
    \item \textbf{Microservices:} Spring Cloud (Config Server, Eureka Service Discovery), API Gateway, Resilience4j
    \item \textbf{Messaging:} Apache Kafka
    \item \textbf{Databases:} SQL
    \item \textbf{DevOps:} Docker, Kubernetes
    \item \textbf{Monitoring \& Logging:} Splunk, Grafana
    \item \textbf{Architecture:} Microservices, REST APIs, Event-Driven Architecture
    \item \textbf{Tools:} Git, GitLab, Postman, Jira
    \item \textbf{Methodologies:} Agile, Scrum
\end{itemize}

\end{document}
